\sysfull

### 2018-08-06 paper/asplos19/relatedwork.tex
chopping down related work (left for now but we might still cut some)

\textbf{Checkpointing-based Systems.} Early work on energy-harvesting runtimes, such as Dewdrop~\cite{dewdrop}, assumed simple computations that complete on a predictable burst of energy. Eon~\cite{sorber_sensys_2007} has scheduled such computation based on priority. Support for computation that spans power failures was first achieved with statically-placed conditional checkpoints in Mementos~\cite{mementos}. Mementos left the possibility of non-volatile state becoming inconsistent with volatile state saved in the checkpoint, rendering in-place writes to data structures in non-volatile memory unsafe~\cite{mspcdino}. DINO~\cite{dino} addressed the consistency problem by selectively versioning non-volatile state within the checkpoints. Ratchet~\cite{ratchet} ensured consistency by placing a checkpoint at the beginning of each idempotent region in the code. Ratchet has a similar technique to task splitting with some essential differences: (i) It does not need to handle non-volatile memory accesses, since it assumes a unified non-volatile memory, whereas \sys has to save the volatile pages in non-volatile memory; (ii) The checkpoint is of a fixed size, while \sys privatize variant number of memory pages.  Clank~\cite{hicks_isca_2017} ensured consistency with custom hardware that dynamically tracks read-after-write dependencies in memory accesses and checkpoints on demand. The consistency problem was also approached with a combination of undo and redo logging in software~\cite{baghsorkhi_cgo_2018}. Just-in-time checkpointing, such as Quickrecall~\cite{quickrecall} and Hibernus++~\cite{hibernusplusplus}, eschews inconsistency by saving all volatile state immediately before power failure and halting the execution. Unlike \sys, such systems rely on introspection hardware to monitor supply voltage and on accurate worst-case bounds on checkpoint cost.

@@

\textbf{Task Decomposition.} In contrast to \sys's construction of coalesced tasks at runtime, prior work has proposed to optimize task size at compile time. CleanCut~\cite{cleancut_2018} program analysis statically estimated energy consumption and split the program into tasks until all tasks consumed less energy than the device can store. An alternative program analysis~\cite{baghsorkhi_cgo_2018} generated different versions of a program with different task sizes and empirically selected the best among them~\cite{baghsorkhi_cgo_2018}.

HarvOS~\cite{mottola2017harvos} takes a hybrid approach that uses a program analysis to place a minimal number of conditional checkpoints that test the energy level at runtime before copying state, like Mementos~\cite{mementos}.

Unlike \sys, such compiler-based approaches, face the challenge of statically predictiong energy consumption of arbitrary input-dependent code with peripheral access, which is an problem without a general solution. Furthermore, a static decomposition approach prevents portability across devices with different storage capacitors. In contrast, \sys avoids forcing any assumptions at compile time and adapts to energy storage capacity and incoming energy conditions at runtime.

>>>>

\textbf{Checkpointing-based Systems.} Early work on energy-harvesting runtimes, such as Dewdrop~\cite{dewdrop}, assumed simple computations that complete on a predictable burst of energy.
%
%Eon~\cite{sorber_sensys_2007} has scheduled such computation based on priority.
%
Support for computation that spans power failures was first achieved with statically-placed conditional checkpoints in Mementos~\cite{mementos}. 
%Mementos left the possibility of non-volatile state becoming inconsistent with volatile state saved in the checkpoint, rendering in-place writes to data structures in non-volatile memory unsafe~\cite{mspcdino}. 
DINO~\cite{dino} addressed the consistency problem by selectively versioning non-volatile state within the checkpoints. Ratchet~\cite{ratchet} ensured consistency by placing a checkpoint at the beginning of each idempotent region in the code. Ratchet has a similar technique to task splitting with the core difference: the checkpoint is of a fixed size, while \sys privatize variant number of memory pages.
%
%Ratchet has a similar technique to task splitting with some essential differences: (i) It does not need to handle non-volatile memory accesses, since it assumes a unified non-volatile memory, whereas \sys has to save the volatile pages in non-volatile memory; (ii) The checkpoint is of a fixed size, while \sys privatize variant number of memory pages. 
%
Clank~\cite{hicks_isca_2017} ensured consistency with custom hardware that dynamically tracks read-after-write dependencies in memory accesses and checkpoints on demand. The consistency problem was also approached with a combination of undo and redo logging in software~\cite{baghsorkhi_cgo_2018}. Just-in-time checkpointing, such as Quickrecall~\cite{quickrecall} and Hibernus++~\cite{hibernusplusplus}, eschews inconsistency by saving all volatile state immediately before power failure and halting the execution. Unlike \sys, such systems rely on introspection hardware to monitor supply voltage and on accurate worst-case bounds on checkpoint cost.

@@

\textbf{Task Decomposition.} In contrast to \sys's construction of coalesced tasks at runtime, prior work has proposed to optimize task size at compile time. CleanCut~\cite{cleancut_2018} program analysis statically estimated energy consumption and split the program into tasks until all tasks consumed less energy than the device can store. An alternative program analysis~\cite{baghsorkhi_cgo_2018} generated different versions of a program with different task sizes and empirically selected the best among them~\cite{baghsorkhi_cgo_2018}. HarvOS~\cite{mottola2017harvos} takes a hybrid approach that uses a program analysis to place a minimal number of conditional checkpoints that test the energy level at runtime before copying state, like Mementos~\cite{mementos}. Unlike \sys, such compiler-based approaches, face the challenge of statically predicting energy consumption of arbitrary input-dependent code with peripheral access, which is an problem without a general solution. Furthermore, a static decomposition approach prevents portability across devices with different storage capacitors. In contrast, \sys avoids forcing any assumptions at compile time and adapts to energy storage capacity and incoming energy conditions at runtime.
